tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-04-29 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Save Qusage results

```{r load_packages}
library('dplyr')
library('readr')
library('readxl')
library('data.table')
library('tibble')
library('qusage')
library('ggplot2')
library('stringr')
library('RColorBrewer')
```

@@

chrom_list <- lapply(unique(pir_info$chrom), 
                     function(chrom_nam) filter(pir_info, 
                                                chrom == chrom_nam)$Geneid)

names(chrom_list) <- paste0('chr', 
                            unique(pir_info$chrom))

#Remove groups with only three members or fewer.
chrom_list <- chrom_list[unlist(lapply(chrom_list, function(x) length(x) > 3))]

@@

```{r}
maleGam_v_Asex.Mix.results <- lapply(
  list(pir_geneset,
    subfam_list, 
    ShortLong_list, 
    chrom_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Gam.Male-Asex.Mixed',
                                gene_list,
                                n.points = 2^18)

@@

    list(results = qs.results.subfam, 
         qstable = qsTable(qs.results.subfam) %>% 
           mutate(contrast = qs.results.subfam$contrast))
  }
)
names(maleGam_v_Asex.Mix.results) <- c('all', 'subfam', 'SorL', 'chrom')

plotGeneSetDistributions(maleGam_v_Asex.Mix.results$SorL$results, path.index =  'S')
plotGeneSetDistributions(maleGam_v_Asex.Mix.results$SorL$results, path.index = 'L')
plotGeneSetDistributions(maleGam_v_Asex.Mix.results$subfam$results, path.index = 'S4')
mutate(maleGam_v_Asex.Mix.results$subfam$qstable , adjust = p.adjust(p.Value, method = 'fdr'))
plotGeneSetDistributions(maleGam_v_Asex.Mix.results$chrom$results, path.index = 'chr14')
```

```{r}
maleGam_v_Liv.Meroz.results <- lapply(
  list(pir_geneset,
    subfam_list, 
    ShortLong_list, 
    chrom_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Gam.Male-Liv.Meroz',
                                gene_list,
                                n.points = 2^18)

@@

```{r}
Asex.Mix_v_Liv.Meroz.results <- lapply(
  list(pir_geneset,
    subfam_list, 
    ShortLong_list, 
    chrom_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Asex.Mixed-Liv.Meroz',
                                gene_list,
                                n.points = 2^18)

@@

    list(results = qs.results.subfam, 
         qstable = qsTable(qs.results.subfam) %>% 
           mutate(contrast = qs.results.subfam$contrast))
  }
)
names(Asex.Mix_v_Liv.Meroz.results) <- c('all', 'subfam', 'SorL', 'chrom')

@@

```{r}
berghei_comparison_stats_df
```

>>>>

```{r load_packages}
library('dplyr')
library('readr')
library('readxl')
library('data.table')
library('tibble')
library('qusage')
library('ggplot2')
library('stringr')
library('RColorBrewer')
library('writexl')
```

@@

@@

```{r}
maleGam_v_Asex.Mix.results <- lapply(
  list(pir_geneset,
    subfam_list, 
    ShortLong_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Gam.Male-Asex.Mixed',
                                gene_list,
                                n.points = 2^18)

@@

    list(results = qs.results.subfam, 
         qstable = qsTable(qs.results.subfam) %>% 
           mutate(contrast = qs.results.subfam$contrast))
  }
)
names(maleGam_v_Asex.Mix.results) <- c('all', 'subfam', 'SorL')

plotGeneSetDistributions(maleGam_v_Asex.Mix.results$SorL$results, path.index =  'S')
plotGeneSetDistributions(maleGam_v_Asex.Mix.results$SorL$results, path.index = 'L')
plotGeneSetDistributions(maleGam_v_Asex.Mix.results$subfam$results, path.index = 'S4')
mutate(maleGam_v_Asex.Mix.results$subfam$qstable , adjust = p.adjust(p.Value, method = 'fdr'))
```

```{r}
maleGam_v_Liv.Meroz.results <- lapply(
  list(pir_geneset,
    subfam_list, 
    ShortLong_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Gam.Male-Liv.Meroz',
                                gene_list,
                                n.points = 2^18)

@@

```{r}
Asex.Mix_v_Liv.Meroz.results <- lapply(
  list(pir_geneset,
    subfam_list, 
    ShortLong_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Asex.Mixed-Liv.Meroz',
                                gene_list,
                                n.points = 2^18)

@@

    list(results = qs.results.subfam, 
         qstable = qsTable(qs.results.subfam) %>% 
           mutate(contrast = qs.results.subfam$contrast))
  }
)
names(Asex.Mix_v_Liv.Meroz.results) <- c('all', 'subfam', 'SorL')

@@

```{r save_xlsx}
 bind_rows(
  lapply(c(maleGam_v_Asex.Mix.results, 
           maleGam_v_Liv.Meroz.results, 
           Asex.Mix_v_Liv.Meroz.results,
           maleVfemale, 
           post48livvearlyliv, 
           livmero_livpost48.results),
         getElement,
         'qstable')
) %>% 
  select(contrast, everything()) %>% 
  mutate(FDR = p.adjust(p.Value, method = 'fdr')) %>% 
  arrange(contrast, pathway.name) %>% 
  write_xlsx(path = 'SupplementaryInformation_Stats_Qusage_berghei.xlsx')
```
